Automated Synthesis of State-Space Digital Systems

### 2016-12-28 cav2017/cav2017.tex
Fixed Fig 2

\begin{figure}
\centering
\hspace*{-1cm}
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.2cm, column sep=.2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \&\node[fill=yellow!20,align=center] (pre) {{\sc 1. pre-}\\{\sc processing}};
   \& \node[fill=yellow!20,align=center] (abstract) {\sc 4. abstraction};
        \node[draw=none] (FIK) at ([xshift=2.5cm,yshift=.3cm]abstract)  {\sc $\Psi (\mat{K})$};
   \& \node[fill=yellow!20,align=center] (counter) {\sc counterexample};\\
   \& 
   \& \node[fill=yellow!20,align=center, minimum width=3cm] (synth) {\sc 2. synthesiser};
       \node[draw=none] (KL) at ([xshift=2.5cm,yshift=-.25cm]synth)  {\sc $\mat{K},\mat{L}$};
       \node[draw=none] (NKL) at ([xshift=2cm,yshift=1cm]synth)  {\sc $P_a$};
   \& \node[fill=yellow!20,align=center, minimum width=4cm] (verify) {\sc 3. verifier ($\Psi$)};
       \node[draw=none] (VUNS) at ([xshift=.6cm,yshift=1cm]verify)  {\sc UNSAT};
       \node[draw=none] (SAT) at ([xshift=2.5cm,yshift=-.3cm]verify)  {\sc SAT};
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
   \&
   \& complexnode/.pic={
     \coordinate (auxsynth);
     \node[draw,rectangle,align=center] (KSAT) at ([xshift=-.8cm]auxsynth.center) {\sc Prog.\\Search};
     \node[draw,rectangle,align=center] (LSAT) at ([xshift=.8cm]auxsynth.center) {\sc Prog.\\Search};
     \node[draw=none] (SATK) at ([xshift=-.5cm,yshift=1.5cm]KSAT)  {$\mathcal{J}_K$};
     \node[draw=none] (K) at ([xshift=.4cm,yshift=1.5cm]KSAT)  {$\tilde{\mat{K}}$};
     \node[draw=none] (SATL) at ([xshift=-.5cm,yshift=1.5cm]LSAT)  {$\mathcal{J}_L$};
     \node[draw=none] (L) at ([xshift=.4cm,yshift=1.5cm]LSAT)  {$\tilde{\mat{L}}$};
    }
   \& complexnode/.pic={
     \coordinate (AA);
     \node[draw,rectangle,align=center] (AAI) at ([xshift=-1.5cm]AA.center) {\sc AI\\Model};
     \node[draw,rectangle,align=center] (AAV) at ([xshift=1.5cm]AA.center) {\sc AA\\Solver};
     \node[draw=none] (AB) at ([xshift=.4cm,yshift=1.5cm]AAI.center)  {\sc $\mat{A}_t$ $\mat{B}_{tp}$ $\mat{B}_{tn}$};     
     \node[draw=none] (MA) at ([yshift=.2cm]AA.center)  {$\mathcal{A}_t$};     
     \node[draw=none] (MB) at ([yshift=-.3cm]AA.center)  {$\mathcal{B}_{tp},\mathcal{B}_{tn}$}; 
     \node[draw=none] (AB) at ([xshift=0.3cm,yshift=1.5cm]AAV.center)  {\sl $\hat{X}^\#$};  
    }\\
   \&
   \& complexnode/.pic={
     \coordinate (UNSAT);
     \coordinate (KUNSAT)  at ([xshift=-.8cm]UNSAT.center);
     \coordinate (LUNSAT) at ([xshift=.8cm]UNSAT.center);
     \node[draw=none] (UNSATB) at ([xshift=1.6cm,yshift=.3cm]UNSAT)  {\sc UNSAT};
  }
  \& \& \coordinate (FAIL);\\
  };
  \path
    (pre.east) edge (abstract.west)
    (abstract.south) edge (synth.north)
    (synth.east) edge (verify.west)
    (verify.east) edge (done.west);
  \path
    ([xshift=+.6cm]KSAT.north) edge ([xshift=-2.1cm]synth.south) 
    ([xshift=-3.3cm]synth.south) edge ([xshift=-.6cm]KSAT.north)
    ([xshift=.6cm]LSAT.north) edge ([xshift=3.3cm]synth.south)
    ([xshift=+2.1cm]synth.south) edge ([xshift=-.6cm]LSAT.north)
    ([xshift=-4.9cm]verify.south) edge (AAI.north)
    (AAI.east) edge (AAV.west)
    (AAV.north) edge ([xshift=4.9cm]verify.south)
    (verify.north) edge (counter.south)
    (counter.west) edge (abstract.east)
    (counter.south west) edge (synth.north east)
    (FAIL.north) edge (done.south);
   \path[-] 
     (KSAT.south) edge (KUNSAT.north)
     (LSAT.south) edge (LUNSAT.north)
     (KUNSAT.east) edge (LUNSAT.west)
     (LUNSAT.east) edge (FAIL.west);
\end{tikzpicture}
\caption{The CEGIS loop with CEGAR\label{fig:CEGARIS}.}
\end{figure}

>>>>

\begin{figure}
\hspace*{-1cm}
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.8cm, column sep=.2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \&\node[fill=yellow!20,align=center] (pre) {{\sc 1. pre-}\\{\sc processing}};
   \& \node[fill=yellow!20,align=center] (abstract) {\sc 4. abstraction};
       % \node[draw=none] (FIK) at ([xshift=2.5cm,yshift=.3cm]abstract)  {\sc $\Psi (\mat{K})$};
   \& \coordinate (aux); \\ % \node[fill=yellow!20,align=center] (counter) {\sc counterexample};\\
   \& 
   \& \node[fill=yellow!20,align=center, minimum width=3cm] (synth) {\sc 2. synthesiser};
       %\node[draw=none] (KL) at ([xshift=2.5cm,yshift=-.25cm]synth)  {\sc $\mat{K},\mat{L}$};
       %\node[draw=none] (NKL) at ([xshift=2cm,yshift=1cm]synth)  {\sc $P_a$};
   \& \node[fill=yellow!20,align=center, minimum width=4cm] (verify) {\sc 3. verifier ($\Psi$)};
       %\node[draw=none] (VUNS) at ([xshift=.6cm,yshift=1cm]verify)  {\sc SAT};
       \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc UNSAT};
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
   \&
   \& complexnode/.pic={
     \coordinate (auxsynth);
     \node[draw,rectangle,align=center] (KSAT) at ([xshift=-.8cm]auxsynth.center) {\sc Prog.\\Search};
     \node[draw,rectangle,align=center] (LSAT) at ([xshift=.8cm]auxsynth.center) {\sc Prog.\\Search};
     \node[draw=none] (SATK) at ([xshift=-.5cm,yshift=1.5cm]KSAT)  {$\mathcal{J}_K$};
     \node[draw=none] (K) at ([xshift=.4cm,yshift=1.5cm]KSAT)  {$\tilde{\mat{K}}$};
     \node[draw=none] (SATL) at ([xshift=-.5cm,yshift=1.5cm]LSAT)  {$\mathcal{J}_L$};
     \node[draw=none] (L) at ([xshift=.4cm,yshift=1.5cm]LSAT)  {$\tilde{\mat{L}}$};
    }
   \& complexnode/.pic={
     \coordinate (AA);
     \node[draw,rectangle,align=center] (AAI) at ([xshift=-1.5cm]AA.center) {\sc AI\\Model};
     \node[draw,rectangle,align=center] (AAV) at ([xshift=1.5cm]AA.center) {\sc AA\\Solver};
     \node[draw=none] (AB) at ([xshift=.4cm,yshift=1.5cm]AAI.center)  {\sc $\mat{A}_t$ $\mat{B}_{tp}$ $\mat{B}_{tn}$};     
     \node[draw=none] (MA) at ([yshift=.2cm]AA.center)  {$\mathcal{A}_t$};     
     \node[draw=none] (MB) at ([yshift=-.3cm]AA.center)  {$\mathcal{B}_{tp},\mathcal{B}_{tn}$}; 
     \node[draw=none] (AB) at ([xshift=0.3cm,yshift=1.5cm]AAV.center)  {\sl $\hat{X}^\#$};  
    }\\
   \&
   \& complexnode/.pic={
     \coordinate (UNSAT);
     \coordinate (KUNSAT)  at ([xshift=-.8cm]UNSAT.center);
     \coordinate (LUNSAT) at ([xshift=.8cm]UNSAT.center);
     \node[draw=none] (UNSATB) at ([xshift=1.6cm,yshift=.3cm]UNSAT)  {\sc UNSAT};
  }
  \& \& \coordinate (FAIL);\\
  };
  \path
    (pre.east) edge (abstract.west)
    (abstract.south) edge (synth.north)
    %([yshift=2em]synth.east) edge node {Candidate} ([yshift=2em]verif.west)
    %([yshift=-2em]verif.west) edge node {New input} ([yshift=-2em]synth.east)
    %([yshift=2em]synth.east) edge node[xshift=-0.7em] {Candidate} ([yshift=2em]verif.west)
    %([yshift=-2em]verif.west) edge node[xshift=-0.7em] {New input} ([yshift=-2em]synth.east)
    ([yshift=1em]synth.east) edge node {$\mat{K},\mat{L}$} ([yshift=1em]verify.west)
    ([yshift=-1em]verify.west) edge node {$P_a$} ([yshift=-1em]synth.east)
    (aux) edge (abstract.east) 
    (verify.east) edge (done.west);
  \path
    ([xshift=+.6cm]KSAT.north) edge ([xshift=-2.1cm]synth.south) 
    ([xshift=-3.3cm]synth.south) edge ([xshift=-.6cm]KSAT.north)
    ([xshift=.6cm]LSAT.north) edge ([xshift=3.3cm]synth.south)
    ([xshift=+2.1cm]synth.south) edge ([xshift=-.6cm]LSAT.north)
    ([xshift=-4.9cm]verify.south) edge (AAI.north)
    (AAI.east) edge (AAV.west)
    (AAV.north) edge ([xshift=4.9cm]verify.south)
    %(verify.north) edge (counter.south)
    %(counter.west) edge (abstract.east)
    %(counter.south west) edge (synth.north east)
    (FAIL.north) edge (done.south);
   \path[-] 
     (KSAT.south) edge (KUNSAT.north)
     (LSAT.south) edge (LUNSAT.north)
     (KUNSAT.east) edge (LUNSAT.west)
     (verify.north) edge node {$\Psi (\mat{K})$} (aux)
     (LUNSAT.east) edge (FAIL.west);
\end{tikzpicture}
\caption{The CEGIS loop with abstraction refinement\label{fig:CEGARIS}.}
\end{figure}
